### 2017-11-22 manuscript.rmd
fixed typo, Casey's email

Catriona Munro^1^, Stefan Siebert^1,2^, Felipe Zapata^1,3^, Mark Howison^4^, Alejandro Damian Serrano^1,9^, Samuel H Church^1, 5^, Freya Goetz^1,6^, Phil Pugh^7^, Steven H.D. Haddock^8^, Casey W. Dunn^1,9^*

@@

\* Corresponding author, casey.dunn@yale.edu

>>>>

Catriona Munro^1^\*, Stefan Siebert^1,2^\*, Felipe Zapata^1,3^, Mark Howison^4^, Alejandro Damian Serrano^1,9^, Samuel H Church^1,5^, Freya Goetz^1,6^, Phil Pugh^7^, Steven H.D. Haddock^8^, Casey W. Dunn^1,9^**

@@

\* Authors contributed equally

\*\* Corresponding author, casey.dunn@yale.edu
